CLT item selection

### 2022-04-25 analysis/clt_item_selection.Rmd
Implement random resets in simualted annealing loop, expose some parameters.

simulated_annealing <- function(k) {
  easiness <- filter(model_params, nlpar=="Easiness") %>% pull(Estimate)
  easy_spread <- model_params%>%filter(nlpar=="Easiness")%>%mutate(width = abs(Q97.5 - Q2.5)) %>% pull(width)
  discrimination <- filter(model_params, nlpar=="Discrimination") %>% pull(Estimate)
	N <- length(easiness)

	best_subset <- sample(c(rep(TRUE, k), rep(FALSE, N-k)))
	best_score <- score_fn(best_subset)

	temp <- 100
	rejected <- 0
	for(i in 1:1e6) {
		new_subset <- proposal_fn(best_subset)
		new_score <- score_fn(new_subset)
		accept_decrease <- rbernoulli(1, temp / 100)
		if(new_score > best_score | accept_decrease) {
			best_subset <- new_subset
			best_score <- new_score
			#print(best_score)
		} else {
			rejected <- rejected + 1
		}
		if(rejected == 10000) {
			break
		}
		temp <- temp*0.999
	}
	#print(best_score)
	ret <- tibble(best_subset = list(best_subset), 
	              best_score = best_score)

>>>>

simulated_annealing <- function(k, cooling_ratio=0.999, reset_thresh=1000, break_thresh=10000) {
  easiness <- filter(model_params, nlpar=="Easiness") %>% pull(Estimate)
  easy_spread <- model_params%>%filter(nlpar=="Easiness")%>%mutate(width = abs(Q97.5 - Q2.5)) %>% pull(width)
  discrimination <- filter(model_params, nlpar=="Discrimination") %>% pull(Estimate)
	N <- length(easiness)

	current_subset <- sample(c(rep(TRUE, k), rep(FALSE, N-k)))
	best_subset <- current_subset
	best_score <- score_fn(best_subset)

	temp <- 100
	rejected <- 0
	no_new_bests <- 0
	for(i in 1:1e6) {
		# Score new subset, and toss a coin
		new_subset <- proposal_fn(current_subset)
		new_score <- score_fn(new_subset)
		accept_decrease <- rbernoulli(1, temp / 100)

		# Accept the new subset if it's an improvement, or if our
		# cooling coin came up heads.
		if(new_score > best_score | accept_decrease) {
			current_subset <- new_subset
			rejected <- 0
			if(new_score > best_score) {
				best_subset <- new_subset
				best_score <- new_score
				no_new_bests <- 0
			} else {
				no_new_bests <- no_new_bests + 1
			}
		# Quit if we've had too many rejections in a row.
		} else {
			rejected <- rejected + 1
			no_new_bests <- no_new_bests + 1
			if(rejected == break_thresh) {
				print(best_score)
				return(best_subset)
			}
		}
		# Start random resets to the current best subset if we haven't
		# found anything better in quite a while.
		if(no_new_bests > reset_thresh & rbernoulli(1, 1/100)) {
			current_subset <- best_subset
		}

		# Cool it!
		temp <- temp*cooling_ratio
	}
	#print(best_score)
	ret <- tibble(best_subset = list(best_subset), 
	              best_score = best_score)
